### 2023-02-24 manuscript.Rmd
Update manuscript.Rmd

## ID 7: Contributor Roles and Involvement
<!-- Larger software project, but the same effort of the individual researcher leads to lower scores? -->

>>>>

## ID 7: Contributor Roles and Involvement

We support the standardised assessment of project contributor roles, similar to the Contributor Roles Taxonomy (CRediT; https://credit.niso.org). 
However, we like to point out that the current evaluation schemes yields lower scores for the same effort of the individual researcher if they are part of a larger software project.
